Accelerating structure–function mapping using the ViVa webtool to mine natural variation

### 2018-11-21 manuscript/02-results.Rmd
Added the app figure to the results section. also added a sub-section "ViVa R Package"

## An introduction to ViVa

@@

**Morgan will provide screenshots**

@@

### Accession mapping
The SNP Mapping tab plots the location of accessions on a world map, and colors the points based on selected variants.

@@

### Alignment
The Alignment tab provides DNA and amino acid sequence alignments of selected genes, with loci colored by variants present. The content of this tab is most useful if the selected genes are all family members or have significant sequence homology. If annotation files are uploaded, the background of the sequences will be colored by annotation region. Hovering the mouse over sequence elements with polymorphisms will provide additional details about the SNP present at that loci.

### Gene tree

### SNP browser
The Browser tab provides a way to search and filter the contents of the VCF file by different fields. After selecting the transcripts to include, a number of filters can be applied to the dataset to match text values, or set min and max limits on the values of numeric fields. When these filters are applied, the table below will update to only contain rows meeting the criteria for all filters.

>>>>

## An overview of ViVa

@@

```{r}
appFigCaption <- "(ref:app_figure_elements) \n **Key elements of the web application** (a) The first section contains two collapsible panels and is used to input information about the genes to be investigated. (b) The SNP Stats tab provides gene level counts and statistics on SNPs. (c) The Diversity Plot tab plots the nucleotide diversity of SNP sites along the length of the coding region of a selected gene. (d) The SNP Mapping tab plots accessions on a world map colored to indicate what SNPs they have. (e) The  Browser tab allows searching for and filtering variants by text and numeric fields. (f) The Alignments tab aligns DNA and RNA sequences of homologous genes, and colors sequence elements based on SNPs and annotations."
```

```{r, echo = FALSE, fig.cap = appFigCaption, out.width="100%"}
knitr::include_graphics("app_figure/App_figure.png")
```

@@

### Accession mapping: View distribution of SNPs across the globe
The SNP Mapping tab plots the location of accessions on a world map, and colors the points based on selected variants.

@@

### SNP browser: Filter and Search for Variants
The Browser tab provides a way to search and filter the contents of the VCF file by different fields. After selecting the transcripts to include, a number of filters can be applied to the dataset to match text values, or set min and max limits on the values of numeric fields. When these filters are applied, the table below will update to only contain rows meeting the criteria for all filters.

### Alignment: Visualize SNPs on alignments of homologous genes
The Alignment tab provides DNA and amino acid sequence alignments of selected genes, with loci colored by variants present. The content of this tab is most useful if the selected genes are all family members or have significant sequence homology. If annotation files are uploaded, the background of the sequences will be colored by annotation region. Hovering the mouse over sequence elements with polymorphisms will provide additional details about the SNP present at that loci.

### ViVa R package: Programmatic access to ViVa's functionality
All of the functionality of the ViVa web application are implemented through function calls to the ViVa R package. In addition to being able to  generate all figures and tables the web application can, users of the R package gain direct access to the underlying data structures and greater controll over parameters when processing and visualizing that data. The ViVa R package can be found at https://github.com/wrightrc/r1001genomes, or installed by typing the line 
`devtools::install_github("wrightrc/r1001genomes")` into an R console.
